Conservator's Corner

### 2018-01-14 pnsac/newsletter/article_EditorsNotes.tex
Draft 3--sent to Roger for review.
New content for Jan 2018 Vol 14, issue 1.

As the President has noted the Association has, through its volunteers,
expended thousands of hours on the North Star's restoration since 2004. In the
last couple of years, however, various developments at CASM have resulted in a
diminution in the amount of restoration work we have been able to do. The result
has been a decline in the number of volunteers working on the aircraft, and a
corresponding decline in our membership. This in turn has led to an overall
decline in the Association's activities, including the publication of this
newsletter. CASM has made some major changes to its personnel, including those
directly responsible for the restoration of the North Star. The Association is
already experiencing a positive change in its relationship with the Museum which
can only be to the good. We look forward to a renewed partnership with CASM to
our mutual benefit.

%\vspace{12pt}

>>>>

Our Association was incorporated in 2003. We are fortunate that a
number of the original members of the organization, such as Tim
Timmins, are still involved as they can provide an historical
perspective. As Tim says, in the article "Our Members," there have been
many bumps in the road, and the fact that the aircraft is still a long
way from completion after 16 years speaks for itself. In January 2017,
R\'{e}jean (Rej) Demers took up his position as CASM's Conservation Project
Manager. Rej's first contribution to the Chronicle can be found in the
"Conservator's Corner." The restoration of the North Star is a priority
for Rej. He has spent the first year of his mandate gathering
information and developing systems and procedures which will, in the
long run, move the restoration of the aircraft forward in a coherent
manner. I have previously stated the obvious and that is the health and
vigour of the Association is dependent on the restoration status of the
aircraft. In the last few years there have been as many bumps in the
road as there are potholes in Ottawa in the spring. The President is
very optimistic we have reached a real turning point (see the
"President's Notes") and wouldn't that be great.

### 2018-01-14 pnsac/newsletter/article_MemberInterview.tex
New content for Jan 2018 Vol 14, issue 1.

\title{Our Members}
\author{Interview with Jm Riddoch}

@@

\begin{quotation}
	\textit{Jim Riddoch is one of the earliest and longest serving members of the
Association. He has made a significant contribution to the operations of the
Association including working on the aircraft as well as being an officer and
member of the board of directors. Although officially retired from formal
positions in the organization, he can still be counted on to help out when
needed.}
\end{quotation}

@@

I started with English Electric Aviation Company in 1956 as an
apprentice technician eventually being assigned to the Mechanical
Engineering Department as a fuel systems technician. I remained there
for 5 years until I was 28 years old and married with a daughter. After
immigrating to Canada in March 1966 I joined DeHavilland Spar Division
in Malton and then moved to Montreal with Jarry Hydraulics as a
development engineer. I remained there for 2 years working chiefly on
development proposals for the wing sweep actuators for F111 aircraft
and Boeing's proposed supersonic Concorde.

In 1968 I joined Air Canada as a junior engineer in the Mechanical
Systems Department and assigned as a landing gear technologist until I
achieved Professional Engineer status in 1974. I then moved around
several other departments in engineering and maintenance until I was
promoted to Superintendent of DC9 maintenance. In that capacity I was
involved in the accident investigation into the loss of one aircraft at
Cincinnati.

I eventually returned to engineering as Director of Interior Systems and
Equipment to supervise extensive fleet modifications and new aircraft
acquisitions. I remained in that position until I retired in 1990.
Following a short stint with First Air I was asked to join a newly formed
Canadian Aviation Maintenance Council to standardize aircraft
maintenance trades basic training. I was hired as the Accreditation
Manager to approve various training establishments including schools,
companies and military programs, I eventually also took on the job of
Registration Manager to accept qualified trade technicians.

@@

Following my retirement from the Canadian Aviation Maintenance
Council in 2003 I was approached by Robert Holmgren to participate in
a voluntary program to help restore an the Canadair North Star aircraft
parked outside at the Canada Aviation Museum. Along with Tim
Timmins and a few others we formed a steering committee to approach
the Museum about forming a voluntary work force to assist the museum
staff to restore the aircraft. At first we met with opposition from some
staff members who felt their jobs were being compromised and possible
staff reductions. Slowly we were approved by the Museum staff with
limited supervision and controlled access and work direction. I was
assigned by the Project North Star Association as Chief Engineer of the
project although all work was controlled and supervised by the
Museum's staff manager.

%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   %name of the graphic, without the path AND in EPS format:
%   \includegraphics[scale=0.5]{fwd_cockpit_complete.eps}
%   %caption of the figure 
%   \caption*{\small \em Forward cockpit -- complete.}
%   %label of the figure, which has to correspond to \ref{}:
%   \label{fig:fwd_cockpit_complete}
%\end{figure}

@@

I worked on the Project for 10 years starting in 2003 both as a “hands
on” volunteer as well as a member of the board of directors and officer
of the Association. Generally I put in at least two days per week and
sometimes more.

@@

The chief highlights have been the high level of workmanship of the
volunteers and displaying the aircraft to the public and interested
persons.

@@

Keeping the Museum staff and management on side with our goals
and objectives and recruiting enough new volunteers to keep the
project going.

>>>>

\title{Our Members}
\author{Interview with Austin J Timmins}

@@

%\begin{quotation}
%	\textit{Jim Riddoch is one of the earliest and longest serving members of the
%Association. He has made a significant contribution to the operations of the
%Association including working on the aircraft as well as being an officer and
%member of the board of directors. Although officially retired from formal
%positions in the organization, he can still be counted on to help out when
%needed.}
%\end{quotation}

@@

My aviation experience includes 36 years service in the RCAF and nine
years with the Canadian Aeronautics and Space Institute. In the RCAF I
completed radio navigator training, which included communications,
navigation and air gunner. I later qualified as an airborne
interception navigator . My operational experience includes air
transport, search and rescue and training. My assignments included
Navigation Leader, Aircrew Leader, Squadron Commander, Air Command
Navigator and Deputy Commander (COO) of the Air Transport Group. I
logged 9500 hours , mostly on the following aircraft: Beechcraft,
Dakota, North Star , Mitchell, Yukon, Hercules, and Boeing 707. My
staff assignments in Europe included movement control (traffic
management) for 1 Air Division and a tour at The NATO Defense College
in Rome.

On retirement from the RCAF I participated in a Transport
Canada A Base review of several airports. I then secured full
employment with Canadian Aeronautics and Space Institute as Executive
Director, retiring in 1995.

@@

My involvement with efforts to conserve North Star 17515 predates
Project North Star. Ottawa area members of the 426 Thunderbird Squadron
Association, mostly retired North Star aircrew, met with the National
Aviation Museum staff to express their concern about the state of the
North Star and proposed volunteer involvement in a preservation effort.
These expressions of concern and interest led to a meeting between the
Association representatives, where General Adamson presented a proposal
for the restoration of the aircraft. It was rejected but assurance was
given that the North Star would be first priority when the new hangar
was completed Also a North Star Trust Fund would be established. Robert
Holmgren, an observer at the meeting, then proceeded to develop a
proposal for volunteers to restore the North Star.
%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   %name of the graphic, without the path AND in EPS format:
%   \includegraphics[scale=0.5]{fwd_cockpit_complete.eps}
%   %caption of the figure 
%   \caption*{\small \em Forward cockpit -- complete.}
%   %label of the figure, which has to correspond to \ref{}:
%   \label{fig:fwd_cockpit_complete}
%\end{figure}

@@

I have been involved from the beginning of efforts to establish PNS,
first as a member of a Steering Committee, led by Robert Holmgren,
later, Vice President and then President of PNSAC. My contacts in
aviation provided much needed advice and support, including access to
initial funding for PNSAC.

@@

The highlight of my involvement has to be the establishment of PNS and
PNSAC.

@@

PNS is now in its 16th year. It has been a work in progress with many
bumps along the way. I spent a lot of time and effort, along with other
members of the Executive, evening out these bumps. Establishing and
maintaining effective channels of communication with CASM and CSTM
required constant attention. Much effort was directed to fund raising,
publicity, and, finding volunteers. In the beginning, every date
brought a new challenge.

### 2018-01-14 pnsac/newsletter/article_PresReport.tex
New content for Jan 2018 Vol 14, issue 1.

The last NStar Chronicle was published in June 2016 and since that time we have
continued our work on the aircraft, but at a greatly reduced pace. Last summer
the Museum staged a Star Trek event in the Reserve Hanger which affected our
ability to work on the North Star. We were not asked to suspend our work until
the end of September, unlike in 2014 when preparations for the Star Wars event
were being made. This helped us retain our Restoration volunteers and recruit
two new ones.

At the end of September, Mike Irvin, the Museum's Conservation Special Projects
Manager, retired and we were asked to suspend work on the aircraft until a new
manager was appointed. In January, R\'{e}jean (Rej) Demers was appointed as the new
Special Projects Manager. Our work on the aircraft resumed on January 30th.

When Project North Star was originally formed in 2003, the Association was
treated with considerable scepticism by the Museum. It was felt that restoring
an aircraft of the size and complexity of a North Star, to the exacting
standards of a national museum, was likely to be beyond the capabilities of a
group of volunteers and that the project would probably fail.

We have now completed approximately 70,000 hours of volunteer work over a period
of 14 years, restoring everything we do to what is acknowledged to be a very
high standard. Scepticism is a thing of the past and we are now treated as a
respected and ongoing part of the Museum operations.

Respect must be earned and comes through hard work and in the case of aircraft
restoration work, attention to detail. Our team of volunteers needs guidance
both from the Museum staff and from our own senior volunteers. One volunteer has
been particularly important in helping us the get to the position we are now in.
Last year he reached a milestone only achieved on two other occasions by a
volunteer and in each case the volunteer worked at the Science and Technology
Museum. Our volunteer has worked 10,000 volunteer hours on the North Star and
for most of this time he also acted as our Project Manager for everything except
the engines. Bruce Gemmill probably was not aware that he had reached 10,000
hours when during June, his remarkable contribution was recognized by the Museum
and in a private event he was presented with a certificate and a gift by Cedric
St-Amour, the Museum Corporation Volunteer Co-ordinator.

I have always seen our Association as having multiple roles. First and foremost,
we are restoring a major artifact with our volunteers. Secondly, we show off our
restoration work to the public which in turn brings visitors and revenue into
the Museum and thirdly through our experienced volunteers we help transfer
skills to younger and less experienced volunteers.

Planning our work in conjunction with the Museum management and the Conservation
staff is something we must continuously work at. It is often a fine balancing
act to decide when to do work on the aircraft in relation to when the Museum is
having a major event such as Open Doors Ottawa and Canada Day. I am hoping that
in future we can regularly update our work schedule in conjunction with our
project plan so that we can more readily have the aircraft available for public
viewing at the times when the Museum would like us to do so, without having to
delay our restoration work unnecessarily.

During the last year, we were able to hold two of our successful Lecture Series
events and are planning to hold another one in May of this year. More details of
the next event will be available soon.

I will conclude with an invitation to any of our members not volunteering at
present to come and join us. Although we have a limit on the number of
volunteers who can get their hands dirty working on restoration, we always
welcome others who would like to join us at our events. You will meet other
likeminded people and have an interesting time talking to members of the public.
You do not need to be an expert on aviation or on the North Star to contribute.
You can contact me by email at the address at the end of this newsletter if you
would like to find out more about volunteering.

>>>>

Since the last issue of the NStar Chronicle in March of this year we
have continued to reorganize our volunteer operations under the
leadership of the Museum's Special Projects Manager, R\'{e}jean (Rej)
Demers. We have started a recruitment process for new restoration
volunteers and to date two new people have started work. During the
summer two more permanent Museum staff joined Rej to replace people who
have retired. It is obviously taking time for the new Museum staff to
get to know the complex operations of the Aviation Museum, to get to
know the Project North Star volunteers and assess their various talents
and areas of expertise. Consequently, our summer has been quiet but
steadily productive.

For several reasons it became necessary to reorganize the location of
several major Museum artifacts. This affected the North Star aircraft
which spent the summer outside the Reserve Hanger resulting in some
problems with water ingress and further bird activity. I am pleased to
say that the aircraft is now back inside the hangar.

The Museum is actively supporting Project North Star and trying to
facilitate our restoration work wherever possible and is promoting our
work and future activities. Our Treasurer, Paul Labranche, and I
recently met with the Museum Foundation. The Foundation is the umbrella
organization with responsibility for fundraising and business
development at the three museums, comprising the Museum Corporation,
(Aviation, Science \& Tech and Agriculture). We had a very productive
meeting, which among other things has resulted in the Foundation
deciding to highlight Project North Star in its Fall fundraising mail
out. This type of collaboration is very good for our Association and we
hope as good for the Foundation.

Our biggest challenge at present is to get our website properly
operational again. A couple of our volunteers with website knowledge
have indicated a willingness to do the necessary work and we are hoping
to have the site working and up to date by the time this issue of the
Nstar Chronicle is published.

On December 2nd we held a Members' meeting at the Museum when we were
fortunate to have Jim Mason join us to talk about the restoration of an
early Lockheed aircraft flown by TCA. The meeting was well attended in
a new venue of the Avro Arrow room instead of the Bush Theatre.
Following Jim's interesting presentation, the group moved to the
Museum's Restoration Hangar where Rej talked about the progress of the
North Star restoration and the plans for work in 2018.

One of the initiatives currently underway is to create a visual
timeline of the work already completed on the North Star restoration
and the planned future work to bring the project to completion. It is
anticipated that this visual timeline will be mounted on a display
board for our members and the public to view.

In closing, I am optimistic that 2018 will see increased activity both
in the aircraft restoration work and also within our Association.

### 2018-01-14 pnsac/newsletter/article_ProgReport.tex
Incorporating latest changes after review of DRAFT #3.
New content for Jan 2018 Vol 14, issue 1.

\title{Project Manager's Progress Report}
\subtitle{PNS 2016 Status Update}
\author{Bruce Gemmill}

@@

\section{Nr 4 Engine}
\label{sec:engine_4}

Work has continued on much of the ancillary equipment for the engine. The
supercharger and intercooler have been completed and installed, as well as the
reduction gearbox. The radiators and header tank have been restored and painted, and
two of the three radiator sections have been installed. Restoration work has
begun on the air intake system, and many of the fuel and oil lines.

\begin{figure}[htbp]
   \vspace{2em}
   \centering
   \includegraphics[scale=0.5]{"PNS 007-im2".png}
   \caption*{\small \em Volunteer Peter Trobridge inspecting the air intake fairing from engine \#4 prior to beginning restoration work.}
   \label{fig:engine_no_4_2}
\end{figure}

\begin{figure}[htbp]
   \vspace{2em}
   \centering
   \includegraphics[scale=0.5]{"PNS 003-im3".png}
   \caption*{\small \em Volunteers Robert Desjardins, Bruce Gemmill and Michel Cote hold the refinished coolant tank from engine \#4.  Hours of polishing were required to get the tank to look like new.}
   \label{fig:coolant_tank}
\end{figure}

The starter motor was found to be very corroded, and disassembly and repair not viable. A
new unit has been ordered and will be installed once delivered. The fire
suppression lines are complete and will be installed along with the cowls when
ready. Some of the cowl panels have been restored, although it has been found
that this engine has more corrosion than the other three engines, possibly it
had been in service longer? This has meant that more work is required to
refurbish each of the many panels. We still hope to have this engine ready for
installation by next spring.

\begin{figure}[htbp]
   \vspace{2em}
   \centering
   \includegraphics[scale=0.5]{"PNS 008-im1".png}
   \caption*{\small \em Volunteer Garry Dupont working on the re-assembly of engine \#4.}
   \label{fig:engine_no_4}
\end{figure}

\section{Fuselage and Main Cabin}
\label{sec:main_cabin}

With the aircraft moved outside in March, little work was done in the aircraft
over the winter. Once the temperatures warmed up, we continued work in the main
cabin to prepare for completion of the painting started last year. Repairs to
the rear bulkhead are now complete with the installation of several new pieces
of aluminum to replace corroded ones. A new section of flooring was installed
where the rear washroom was situated. This required replacing about 1000 rivets!

\begin{figure}[htbp]
   \vspace{2em}
   \centering
   \includegraphics[scale=0.5]{"pns 043-im4".png}
   \caption*{\small \em A single new floor panel at the rear of the main cabin required over 1000 rivets.  
   Cleco clips are used to accurately align the panel during riveting.}
   \label{fig:panel_revets}
\end{figure}

Cleaning and corrosion removal continued throughout the cabin. It seems whenever
we feel we are near completion, we find more corrosion. We had also planned to
finish priming the floor and painting the rear bulkhead before the aircraft
returned to the hanger later in the year, but this was delayed by the shutdown
of the project while a new Project Manager was hired by the museum. The wood
floors and walls still need to be repaired, or new panels made, and all will
require painting.

\section{Cabin Liners}
\label{sec:liners}

All the large pieces of liner have either been repaired or replaced, but with
limitations on space, most remaining work on the cabin liners has been
postponed. New window surrounds have also been made, but then all liners will
require painting and stenciling, and this must wait until there is more room in
the shop and the paint booth. Liners were also made for the top of the heater
ducts.

\begin{figure}[htbp]
   \vspace{2em}
   \centering
   \includegraphics[scale=0.5]{P1020369-im5.png}
   \caption*{\small \em One of the refurbished heater duct sections with a new fabric headliner secured to the top. The sides are covered with mica insulation that was removed, cleaned and reattached after repairs to the metal duct. These will be installed in the main cabin.}
   \label{fig:heaters_liners}
\end{figure}

\section{PNS 2017 Update}
\label{sec:pnsupdate}

We were able to restart work on the aircraft in late January, following the
arrival of our new Project manager, Rej Demers. So far, we have completed the
top cowl panels and one of the radiator flaps, which required a repair patch to
the outer skin, and the electrical harnesses, which are now waiting for
painting. Work continues on the air box and the remaining cowl panels.

We have decided not to move the aircraft outside this year. With our efforts
concentrated on completing engine \#4, it is unlikely we would have the resources
to also complete the repair work in the cabin needed to allow for priming and
painting, which is the main reason for moving the aircraft outside in the summer.

>>>>

\title{Conservator's Corner}
%\subtitle{PNS 2016 Status Update}
\author{R\'{e}jean Demers}

@@

\textit{R\'{e}jean Demers (Rej, to those who work with him) is a Transport Canada
licensed Aircraft Maintenance Engineer (AME). R\'{e}jean was a small
business owner in Gatineau QC for over 10 years, working for a wide
variety of private and commercial aircraft owners and operators.
Following a stint in Northern Ontario working on turpoprop freighters
and bulk fuel haulers, he took up his present position as a
Conservator, Special Projects Manager with Ingenium, Canada's Museums
of Science and Innovation in January 2017. His main project is the
restoration of the Canadair North Star DC-4GM at the Canadian Aviation
and Space Museum. He recounts below his introduction to his new job.}

Leaving Pickle Lake was like getting shot out of a cannon in a snow
storm. At that time, Christmas of 2016, I was the last person on my
crew to leave the YPL base, having seen my colleagues off for the end
of our tour and the holidays. After a full day of flying, the fleet had
to be tucked away in the barn ready for service. On Boxing Day, a fresh
crew would fly in and start another two week tour of line maintenance
with the company we worked for. However, on that Christmas, I was
quitting my job.

Nobody knew I was leaving until I got back to the bunkhouse and shared
Christmas dinner with the remaining pilots and ops personnel. I refer
to them in these terms now, but then and there, I could say they were
my friends. In the weeks leading to my departure, no one knew I was
leaving. No one speaks of breaking out of prison when they are behind
bars. The difference being the only bars I saw were the Pickle Lake
Hotel and a watering hole in Thunder Bay called the Apollo.

Driving down the 599 in that snow storm with a truck I had bought for
\$100 was a white knuckle ride. Knowing this would probably be the last
time I drove the 2000km distance between Northern Ontario and home in
Gatineau. The stakes were high: A flight to catch in Ottawa (T-minus
48hrs), New Year's eve in New York city with my family waiting there
for me and a new job starting at CASM on the day of my wedding
anniversary. Could 2017 start with anything less? Arriving to work that
January 3rd morning was a good feeling, until I got startled by "Manny"
the mannequin sitting in my predecessor's office chair. If a sense of
humour was a job requirement, I hoped to get the joke. I would later
find Manny in other compromising positions, some of which I refuse to
admit my participation in writing.

The momentum I have gained in the twelve months since my escape from
Pickle Lake is only part of what keeps me moving forward. I also count
on the support of others, namely co-workers and volunteers. My position
as Project Manager of the North Star restoration relies on the good
work and cooperation of all hands involved. As the work itself proves
to be technical and highly detailed, with wide ranges of abilities
involved, people are always the driving force.

It was suggested my article for the North Star Chronicle be focused on
the restoration of a certain four engined artifact \#1967.0645. For
details on the work that has been carried out by our dedicated group of
volunteers, I recommend you read my conservation report on the subject.
It is available online: \textcolor{blue}{\texttt{\url{http://www.projectnorthstar.ca}}}
or by email: \textcolor{blue}{\email{rdemers@techno-science.ca}}

%\section{Nr 4 Engine}
%\label{sec:engine_4}
%
%Work has continued on much of the ancillary equipment for the engine. The
%supercharger and intercooler have been completed and installed, as well as the
%reduction gearbox. The radiators and header tank have been restored and painted, and
%two of the three radiator sections have been installed. Restoration work has
%begun on the air intake system, and many of the fuel and oil lines. 
%
%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   \includegraphics[scale=0.5]{"PNS 007-im2".png}
%   \caption*{\small \em Volunteer Peter Trobridge inspecting the air intake fairing from engine \#4 prior to beginning restoration work.}
%   \label{fig:engine_no_4_2}
%\end{figure}
%
%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   \includegraphics[scale=0.5]{"PNS 003-im3".png}
%   \caption*{\small \em Volunteers Robert Desjardins, Bruce Gemmill and Michel Cote hold the refinished coolant tank from engine \#4.  Hours of polishing were required to get the tank to look like new.}
%   \label{fig:coolant_tank}
%\end{figure}
%
%The starter motor was found to be very corroded, and disassembly and repair not viable. A
%new unit has been ordered and will be installed once delivered. The fire
%suppression lines are complete and will be installed along with the cowls when
%ready. Some of the cowl panels have been restored, although it has been found
%that this engine has more corrosion than the other three engines, possibly it
%had been in service longer? This has meant that more work is required to
%refurbish each of the many panels. We still hope to have this engine ready for
%installation by next spring. 
%
%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   \includegraphics[scale=0.5]{"PNS 008-im1".png}
%   \caption*{\small \em Volunteer Garry Dupont working on the re-assembly of engine \#4.}
%   \label{fig:engine_no_4}
%\end{figure}
%
%\section{Fuselage and Main Cabin}
%\label{sec:main_cabin}
%
%With the aircraft moved outside in March, little work was done in the aircraft
%over the winter. Once the temperatures warmed up, we continued work in the main
%cabin to prepare for completion of the painting started last year. Repairs to
%the rear bulkhead are now complete with the installation of several new pieces
%of aluminum to replace corroded ones. A new section of flooring was installed
%where the rear washroom was situated. This required replacing about 1000 rivets!
%
%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   \includegraphics[scale=0.5]{"pns 043-im4".png}
%   \caption*{\small \em A single new floor panel at the rear of the main cabin required over 1000 rivets.  
%   Cleco clips are used to accurately align the panel during riveting.}
%   \label{fig:panel_revets}
%\end{figure}
%
%Cleaning and corrosion removal continued throughout the cabin. It seems whenever
%we feel we are near completion, we find more corrosion. We had also planned to
%finish priming the floor and painting the rear bulkhead before the aircraft
%returned to the hanger later in the year, but this was delayed by the shutdown
%of the project while a new Project Manager was hired by the museum. The wood
%floors and walls still need to be repaired, or new panels made, and all will
%require painting. 
%
%\section{Cabin Liners}
%\label{sec:liners}
%
%All the large pieces of liner have either been repaired or replaced, but with
%limitations on space, most remaining work on the cabin liners has been
%postponed. New window surrounds have also been made, but then all liners will
%require painting and stenciling, and this must wait until there is more room in
%the shop and the paint booth. Liners were also made for the top of the heater
%ducts.
%
%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   \includegraphics[scale=0.5]{P1020369-im5.png}
%   \caption*{\small \em One of the refurbished heater duct sections with a new fabric headliner secured to the top. The sides are covered with mica insulation that was removed, cleaned and reattached after repairs to the metal duct. These will be installed in the main cabin.}
%   \label{fig:heaters_liners}
%\end{figure}
%
%\section{PNS 2017 Update}
%\label{sec:pnsupdate}
%
%We were able to restart work on the aircraft in late January, following the
%arrival of our new Project manager, Rej Demers. So far, we have completed the
%top cowl panels and one of the radiator flaps, which required a repair patch to
%the outer skin, and the electrical harnesses, which are now waiting for
%painting. Work continues on the air box and the remaining cowl panels.
%
%We have decided not to move the aircraft outside this year. With our efforts
%concentrated on completing engine \#4, it is unlikely we would have the resources
%to also complete the repair work in the cabin needed to allow for priming and
%painting, which is the main reason for moving the aircraft outside in the summer.
